Project 1 Checkpoint

### 2015-02-27 project1/checkpoint/main.tex
Adding in the acceleration graph
Citing the GA Code

Assuming all cars have length $L$, the $n$th car in the queue will have to travel $L(n-1)$ feet in order to cross the
intersection. Given our closed form above, in order to know how long it will be before a car passes we'll need to solve
\[
p(t) = L(n-1)
\]
Unfortunately, this must be done numerically. The function is fairly well behaved, and will in general have two roots
(only one positive). Using a positive initial guess (around 2 or so, judging by visual inspection), Newton's method will converge
within only a few steps. (SHOW GRAPH)

@@

We also assume here that cars are entering at the same velocity, based off of the urban speed limit of 30 mph set by
the state of Georgia (CITE). Furthermore, we assume a single sized car, based off of the average from the NGSIM data.
Having a constant speed and length allows us to simplify the calculation of stop points for cars entering the
intersection. Although these simplifications help, dealing with acceleration is an even more complex matter. In this
case it is both a mixture of both discrete (the light signal) and continuous elements (the car's velocity). By choosing
an event-driven approach we are forced to simplify acceleration, since we cannot accurately represent a continuous
system in this manner.

>>>>

Assuming all cars have length $L$, the $n$th car in the queue will have to travel $L(n-1)$ feet in order to cross the
intersection. Given our closed form above, in order to know how long it will be before a car passes we'll need to solve
\[
p(t) = L(n-1)
\]
Unfortunately, this must be done numerically. The function is fairly well behaved, and will in general have two roots
(only one positive). Using a positive initial guess (around 2 or so, judging by visual inspection), Newton's method
will converge within only a few steps. \ref{fig:acceleration} demonstrates some properties of this function
$0 = p(t) - L(n-1)$, one being
that as we move further back in the queue, the timing between cars approaches a constant. This is a result of cars
have more space to accerate to full speed.

\begin{figure}
\begin{center}  
\includegraphics[width=4in]{../acceleration.pdf}  
\caption{\small \sl $p(t) - L(n-1)$ for $n \in \{0, 1, 2, 3, 4\}$ \label{fig:acceleration}}  
\end{center}  
\end{figure}

@@

We also assume here that cars are entering at the same velocity, based off of the urban speed limit of 30 mph set by
the state of Georgia \cite{gacode}. Furthermore, we assume a single sized car, based off of the average from the NGSIM data.
Having a constant speed and length allows us to simplify the calculation of stop points for cars entering the
intersection. Although these simplifications help, dealing with acceleration is an even more complex matter. In this
case it is both a mixture of both discrete (the light signal) and continuous elements (the car's velocity). By choosing
an event-driven approach we are forced to simplify acceleration, since we cannot accurately represent a continuous
system in this manner.
